---
title: "Alcohol vs Seat choice"
author: "Adam Ayala"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

The box in the back row has a higher third quartile and the median looks slightly higher than the other boxes third quartile positions. Comparing the Middle and Front boxes we see both have a similar median and third quartile however the Middle box section has much more outliers. The boxes are not disjoint.


## Numerical Summarys

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The front and back seat has around the same number of people while the back seat has more than twice their numbers. This summary shows that while the back seat had 32 people the back seat had a max of 55 drinks which is twice the numbers of the front and middle rows. The average of drinks in the back seat is 9.6 and the drinks for the front seat are about 2 and the beak seat has a mean of around 3.


## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The probability of getting these results are one out of ten thousand as seen by the 0.000116 probability. Telling us that is there is something going on here that is different between the groups. At least 2 of them are different and more investigation is needed.


```{r}
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

The Front-Back and the Middle-Back are very similar, they both have values below 0 showing that there is a difference when compared to the Back. This is seen as the Middle-Front section is above zero showing great correlation with each other.




## Conclusions

A boxplot would show that back row was higher with alcohol consumption than the front and the middle rows. To see what was happening we did a numerical test to see that back row had a mean of 9 higher than the front row of 2 and middle row of 3. With this we did a Inferential result showing a probability of 0.000116. Proving that something is happening in this data. To see what is happening another test is done. This test would compare the different rows individually with each other. With this we can see that the Back row had a higher alcohol consumption than the Front and middle rows. As when the Front and Back row was compared and the Middle and back row it would be negative indicating one of the rows to be greater than the other. While when the Front and Back are compared they are above 0 showing around the same numbers. Proving that the back row has higher consumption than the front row and middle row as it must be the one to make the number negative.
